Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-02 prop_letter.tex
Updates from ShareLaTeX

When $\delta=0$ , every event must be assigned a probability in either
the interval $[0,0]$ or $[1,1]$, i.e., every event is completely
determined with certainty. As $\delta$ gets bigger, the QIVPM allows
more and more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
two possible collection of intervals\nb$\mathscr{I}$ are $\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],\necess\right\} $
and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\} $.
Our technical result will be
that for ``small enough'' $\delta$, a variant of the Kochen-Specker
theorem is still valid. To state and prove this result we will first
reformulate the original Kochen-Specker as a statement regarding the
non-existence of $0$-deterministic QIVPM. We will then strengthen this
result to show the non-existence of any $\delta$-deterministic QIVPM
when $\delta < 1/3$ and the Hilbert space dimension is greater than
2.

>>>>

When $\delta=0$, every event must be assigned a probability in either
interval $[0,0]$ or $[1,1]$, i.e., every event is completely
determined with certainty. As $\delta$ gets larger, the QIVPM allows for
more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
two possible collections of intervals\nb$\mathscr{I}$ could be 
$\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
\necess\right\}$ and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$. Our technical result will be
that for ``small enough'' $\delta$, a variant of the Kochen-Specker
result is still valid. To state and prove this generalization we will first
reformulate the original Kochen-Specker theorem as a statement regarding the
non-existence of $0$-deterministic QIVPM. We will then strengthen this
result to show the non-existence of any $\delta$-deterministic QIVPM
when $\delta < 1/3$ and the Hilbert space dimension is greater than
2.
